\bf On semidefinite representable sets over valuation fields

### 2024-11-19 article/paper_padic_spec.tex
commit by Simone

\begin{proposition}
  %%% OLD STATEMENT
  %%% A polyhedron is a spectrahedron.
A polyhedron in $K^n$ is a spectrahedron in $K^n$.
\end{proposition}
\begin{proof}
  Let $P$ be a polyhedron in $K^n$. We show that there exist $d \in \mathbb{N}$ and
  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = S_A$. Assume $P = L \cap M$ with
  \begin{equation*}
    \begin{aligned}
    L &= \{x \in K^n : \val \ell_i(x) \geq 0, i=1, \ldots, d\} \\
    M &= \{x \in K^n : \val m_j(x) = +\infty, j=1, \ldots, e\}
    \end{aligned}
  \end{equation*}
  for some $d, e \in \mathbb{N}$. Let $\eta \leq n$ be the dimension of $M$ as vector subspace of
  $K^n$, and let $y=(y_1, \ldots, y_\eta) \in K^{\eta}$ be variables on $M$, with $y = Tx$
  for some $T \in K^{\eta \times n}$ with $\text{rank}(T) = \eta$. Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$
  be such that
  $$
  A_0+x_1A_1+\cdots+x_nA_n = \diag(\ell_1(x), \ldots, \ell_d(x)).
  $$
  One has that
  $$
  P = \{x \in \}
  $$
  {\bf à terminer -- Simone}  
%%% OLD PROOF
%  Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
%  be a polyhedron as in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
%  and $L = \{x \in K^n : \val(m_j) = +\infty, j=1,\ldots,e\}$.
%  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in K[x]^{d\times d}_1$,
%  so that $A(x) = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in K^{d\times d}$.
%  We might assume that $A_0,A_1,\ldots,A_n$ are affinely independent, so that the mapping
%  $\varphi(x) = A(x)$ is injective. 
%  First, remark that $Q=S_A$ and thus $\varphi(Q) = \mathcal{L} \cap K^{d\times d}$, with
%  $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$ is a spectrahedron.
%  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$,
%  hence $\varphi(L) \subset K^{d\times d}$ is an affine space. Since $\varphi$ is injective,
%  one has $\varphi(P) = \varphi(Q \cap L) = \varphi(Q) \cap \varphi(L)$ which is the intersection
%  of a spectrahedron with an affine space, thus a spectrahedron.
%  %Define $B = m_1 \oplus \cdots \oplus m_e \in K[x]^{e\times e}_1$
\end{proof}

>>>>

\begin{proposition}
  %%% OLD STATEMENT
  %%% A polyhedron is a spectrahedron.
A polyhedron in $K^n$ is a spectrahedron in $K^n$.
\end{proposition}
\begin{proof}
  Let $P$ be a polyhedron in $K^n$. We show that there exist $d \in \mathbb{N}$ and
  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = S_A$. Assume $P = L \cap M$ with
  \begin{equation*}
    \begin{aligned}
    L &= \{x \in K^n : \val \ell_i(x) \geq 0, i=1, \ldots, d\} \\
    M &= \{x \in K^n : \val m_j(x) = +\infty, j=1, \ldots, e\}
    \end{aligned}
  \end{equation*}
  for some $d, e \in \mathbb{N}$. Let $\eta \leq n$ be the dimension of $M$ as vector subspace of
  $K^n$, and let $y = (y_1, \ldots, y_\eta)^T \in K^{\eta}$ be variables on $M$, with $Ty = x$
  for some $T \in K^{n \times \eta}$ with $\text{rank}(T) = \eta$. Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$
  be such that
  $$
  A_0+x_1A_1+\cdots+x_nA_n = \diag(\ell_1(x), \ldots, \ell_d(x)).
  $$
  One has that
  $$
  P = \{x \in K^n : x \in M, \}
  $$
  {\bf à terminer -- Simone}  
%%% OLD PROOF
%  Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
%  be a polyhedron as in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
%  and $L = \{x \in K^n : \val(m_j) = +\infty, j=1,\ldots,e\}$.
%  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in K[x]^{d\times d}_1$,
%  so that $A(x) = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in K^{d\times d}$.
%  We might assume that $A_0,A_1,\ldots,A_n$ are affinely independent, so that the mapping
%  $\varphi(x) = A(x)$ is injective. 
%  First, remark that $Q=S_A$ and thus $\varphi(Q) = \mathcal{L} \cap K^{d\times d}$, with
%  $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$ is a spectrahedron.
%  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$,
%  hence $\varphi(L) \subset K^{d\times d}$ is an affine space. Since $\varphi$ is injective,
%  one has $\varphi(P) = \varphi(Q \cap L) = \varphi(Q) \cap \varphi(L)$ which is the intersection
%  of a spectrahedron with an affine space, thus a spectrahedron.
%  %Define $B = m_1 \oplus \cdots \oplus m_e \in K[x]^{e\times e}_1$
\end{proof}
